%-------------------------
% Resume in Latex
% Template By : Sourabh Bajaj
% Owner of Resume: Angelo Dominic Domingo
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://jellodomingo.github.io/}{\Large Angelo Dominic Domingo}} & Email : \href{mailto:domingoangelodominic@gmail.com}{domingoangelodominic@gmail.com}\\
  \href{https://jellodomingo.github.io/}{https://jellodomingo.github.io/} & Mobile : \href{tel:+19258763067}{+1-925-876-3067} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Irvine}{Irvine, CA}
      {Bachelor of Science in Computer Science}{Sept. 2016 -- Jan. 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ultra/Mint Mobile}{Costa Mesa, CA / Remote}
      {Software Engineer}{Feb 2022 - Present}
      \resumeItemListStart
        \resumeItem
          {Maintained and developed frontend features in React and Next.js for Ultra and Mint websites, using libraries such as Redux and React Context.}
        \resumeItem
	{Converted vanilla React applications to Next.js 13 and above.}	
       \resumeItem
	{Refactored existing JavaScript classes to Typescript functional components.}
       \resumeItem
	{Implemented backend security features on Express Node.js APIs}
       \resumeItem
	{Created and maintained e2e tests using Cypress and Postman for mock data, and components using Jest. And utilized tests on CI/CD pipelines to maintain code stability.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Unisys}{Irvine, CA - Remote}
      {Security Software Engineer}{Jan 2014 - Oct 2016}
      \resumeItemListStart
	 \resumeItem
	{Developed UI and backend features for the company's Electron-based augmented knowledge discovery tool in Javascript, Node.js, and React.}
	 \resumeItem	
	{Refactored and updated existing Javascript codebase to Typescript.}
	 \resumeItem	
	{Developed and maintained automated tests using Spectron and WebDriverIO to prove stability and functionality. }
	 \resumeItem	
	{Utilized Jenkins to run test suites and builds.}
      \resumeItemListEnd

    \resumeSubheading
      {Mercury Insurance,}{Brea, CA - Remote}
      {Java Developer}{May 2021 - Sept. 2021}
      \resumeItemListStart
	\resumeItem
	{Developed SQL script generator in Java to expedite agency data onboarding  and aid in the ETL process.}
	\resumeItem
	{Resolved production database tickets through SQL scripts and data updates.}
	\resumeItem
	{Maintained and updated agency commission application in Java, Javascript, and HTML.}
	\resumeItem
	{Utilized Jenkins to build and deploy application code to development, QA, and production environments.}
      \resumeItemListEnd

    \resumeSubheading
      {anna}{Boston, MA - Remote}
      {Full-Stack Engineer}{Feb 2021 - May 2021}
      \resumeItemListStart
	\resumeItem
	{Maintained and designed components for React frontend, using a combination of Redux and React's Context API for state management.}
	\resumeItem
	{Utilized Firebase Realtime Database to update status of customer kiosks in real time.}
	\resumeItem
	{Built CI/CD pipelines hosted on AWS using Docker, CodePipeline, and ECS to deploy the company's backend services.}
	\resumeItem
	{Engineered communication protocol between vending machines and backend services using websockets and C\#.}
      \resumeItemListEnd

    \resumeSubheading
      {DealerClick}{Newport Beach, CA }
      {Full-Stack Engineer}{May 2020 - Jan 2021}
      \resumeItemListStart
	\resumeItem
	{Maintained and developed web application features using Java and Java Server Faces that will eventually replace the company's dated VB6 automotive DMS system software.}
	\resumeItem
	{Optimized website load times by upgrading servers from an outdated version of Glassfish to Wildfly.}
	\resumeItem
	{Rewrote existing SQL queries to allow for faster website data load times. }
	\resumeItem
	{Refactored Java API Service from a J2EE monolithic system to Spring Boot microservice architecture.}
	\resumeItem
	{Developed React Native application that allowed for offline and online scanning of inventory barcodes.}
	\resumeItem
	{Spearheaded an overhaul of the dated VB6 automotive DMS system software to a web application using a Spring Boot backend and React.js frontend.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Javascript/Typescript, SQL, Java, Python, }
      \hfill
      \textbf{Technologies}{: Git, React, Nextjs, Node, AWS, Spring Boot, MySQL, Cypress, Jest, Docker, Postman}
    }
  \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
